The quench action approach in finite integrable spin chains

### 2015-12-05 draft/fs_qa_v7.tex
05/12/2015

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Counting and string content of the eigenstates with nonzero N\'eel and 
Majumdar-Ghosh overlap}
\label{app-1}

Here we provide some exact combinatorial formulas for the total number of 
parity-invariant eigenstates of the $XXX$ chain having non-zero overlap with 
the N\'eel state and the Majumdar-Ghosh state. 
%We consider both the situations  
%with constrained and unconstrained string content and particle number (i.e., 
%total magnetization). 
In~\ref{app-1.1} we consider all possible parity-invariant 
eigenstates, whereas in~\ref{app-1.2} we exclude the eigenstates containing 
zero-momentum strings. Note that the result in~\ref{app-1.1} is only an upper 
bound, while the counting in~\ref{app-1.2} is exact. The strategy of the proof 
is the same as that used to count the number of solutions of the 
Bethe-Gaudin-Takahashi equations (see for instance Ref.~\cite{faddeev-1996}).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Allowing the zero-momentum strings}
\label{app-1.1}

Here we prove that the total number of parity-invariant eigenstates $Z_{Neel}$ 
with, in principle, non-zero N\'eel overlap for a chain of length $L$ is given 
as 
%
\begin{equation}
\label{N-count}
Z_{Neel}=2^{\frac{L}{2}-1}+\frac{1}{2}B\Big(\frac{L}{2},\frac{L}{4}\Big)+1. 
\end{equation}
%
We restrict ourselves to the situation with $L$ divisible by four. The strategy to 
prove~\eref{N-count} is to count all the possible parity-invariant BGT quantum numbers 
configurations (cf. section~\ref{sec:1.3}). Let us consider the sector with fixed number 
of particles $M$, and string content ${\mathcal S}=\{s_1,s_2,\dots,s_{M}\}$. Here $s_n$ is 
the number of $n$-strings, with the constraint $\sum_k ks_k=M$. One should stress that 
$M$ is the number of particles corresponding to {\it finite} solutions of the Bethe 
equations. The total number of particles is $L/2$, due to the fact that the N\'eel 
state has $S_T^z=0$. The remaining $L/2-M$ particles correspond to infinite solutions 
of the Bethe equations (see section~\ref{sec:1.2}). It is straightforward to check that the
total number of parity-invariant quantum number pairs ${\mathcal N}_n(L,{\mathcal S})$ 
in the $n$-string sector is given as 
%
\begin{equation}
\label{NnLS}
{\mathcal N}_n(L,{\mathcal S})=\Big\lfloor\frac{L}{2}-\frac{1}{2}
\sum_{m=1}^{M}t_{nm}s_m\Big\rfloor,
\end{equation}
%
where $t_{nm}\equiv 2\textrm{Min}(n,m)-\delta_{n,m}$. Thus, the number of parity-invariant 
eigenstates of the $XXX$ chain ${\mathcal N}(L,{\mathcal S})$ compatible with string content 
${\mathcal S}$ is obtained by choosing in all the possible ways the associated parity-invariant 
quantum number pairs as     
%
\begin{equation}
\label{NLS}
{\mathcal N}(L,{\mathcal S})=\prod_{m=1}^{M} B\left({\mathcal N}_m,\left\lfloor
\frac{s_m}{2}\right\rfloor\right).
\end{equation}
%
Here the product is because each string sector is treated independently, while the 
factor $1/2$ in $s_m/2$ is because since all quantum numbers are organized in pairs, 
only half of them have to be specified. Note that in each $n$-string sector only one 
zero momentum (i.e., zero quantum number) string is allowed, due to the fact that 
repeated solutions of the BGT equation are discarded. Moreover, from~\eref{NnLS} one has 
that $s_m$ is odd (even) only if this zero momentum string is (not) present.

We now proceed to consider the string configurations with fixed particle number $0\le\ell
\le M$ and fixed number of strings $1\le q\le M/2$. Note that the maximum allowed string 
length is $M/2$ because of parity invariance. Note also that in determining $q$, strings 
of different length are treated equally, i.e., $q=\sum_m s_m$. For a given fixed pair 

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Counting and string content of the eigenstates with nonzero N\'eel and 
%Majumdar-Ghosh overlap}
\section{Counting and string content of parity-invariant eigenstates}
\label{app-1}

Here we provide some exact combinatorial formulas for the total number of 
parity-invariant eigenstates of the $XXX$ chain, which are the only eigenstates 
having, in principle, non-zero overlap with the N\'eel state and the 
Majumdar-Ghosh state.

In~\ref{app-1.1} we consider all possible parity-invariant 
eigenstates, whereas in~\ref{app-1.2} we exclude the eigenstates containing 
zero-momentum strings. Note that the result in~\ref{app-1.1} is only an upper 
bound, while the counting in~\ref{app-1.2} is exact. The strategy of the proof 
is the same as that used to count the number of solutions of the 
Bethe-Gaudin-Takahashi equations (see for instance Ref.~\cite{faddeev-1996}).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Allowing the zero-momentum strings}
%\label{app-1.1}

Here we prove that the total number of parity-invariant eigenstates $Z_{Neel}$ 
with, in principle, non-zero N\'eel overlap for a chain of length $L$ is given 
as 
%
\begin{equation}
\label{N-count}
Z_{Neel}=2^{\frac{L}{2}-1}+\frac{1}{2}B\Big(\frac{L}{2},\frac{L}{4}\Big)+1. 
\end{equation}
%
We restrict ourselves to the situation with $L$ divisible by four. The strategy to 
prove~\eref{N-count} is to count all the possible parity-invariant BGT quantum numbers 
configurations (cf. section~\ref{sec:1.3}).

The total number of particles in the eigenstates is fixed to $L/2$, due to the fact that 
the N\'eel state has $S_T^z=0$. As the N\'eel state is not $SU(2)$ invariant the corresponding 
rapidities can be finite (identifying highest-weigth states) or infinite (descendant states).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{$SU(2)$ Highest-weight eigenstates}

Let us consider the eigenstate sector with fixed number of finite rapidities 
$\ell$, the remaining $L/2-\ell$ ones being infinite (see section~\ref{sec:1.2}). 
Let us denote the associate string content as ${\mathcal S}=\{s_1,s_2,\dots,
s_{\ell}\}$. Here $s_n$ is the number of $n$-strings, with the constraint 
$\sum_k ks_k=\ell$. 
Parity-invariant eigenstates are in one-to-one correspondence with parity-invariant 
BGT quantum number configurations. Moreover, it is straightforward to check that 
the total number of parity-invariant quantum number pairs ${\mathcal N}_n(L,{
\mathcal S})$ in the $n$-string sector is given as 
%
\begin{equation}
\label{NnLS}
{\mathcal N}_n(L,{\mathcal S})=\Big\lfloor\frac{L}{2}-\frac{1}{2}
\sum_{m=1}^{\ell}t_{nm}s_m\Big\rfloor,
\end{equation}
%
where $t_{nm}\equiv 2\textrm{Min}(n,m)-\delta_{n,m}$. Thus, the number of parity-invariant 
eigenstates of the $XXX$ chain ${\mathcal N}(L,{\mathcal S})$ compatible with string content 
${\mathcal S}$ is obtained by choosing in all the possible ways the associated parity-invariant 
quantum number pairs as     
%
\begin{equation}
\label{NLS}
{\mathcal N}(L,{\mathcal S})=\prod_{m=1}^{\ell} B\left({\mathcal N}_m,\left\lfloor
\frac{s_m}{2}\right\rfloor\right).
\end{equation}
%
Here the product is because each string sector is treated independently, while the 
factor $1/2$ in $s_m/2$ is because since all quantum numbers are organized in pairs, 
only half of them have to be specified. Note that in each $n$-string sector only one 
zero momentum (i.e., zero quantum number) string is allowed, due to the fact that 
repeated solutions of the BGT equation are discarded. Moreover, from~\eref{NnLS} one has 
that $s_m$ is odd (even) only if this zero momentum string is (not) present.

We now proceed to consider the string configurations with fixed particle number $\ell\le 
L/2$ and fixed number of strings $1\le q\le\ell$. Note that due to parity invariance 
$\ell$ must be even. 
Also, in determining $q$ strings of different length are treated equally, i.e., 
$q=\sum_m s_m$. For a given fixed pair 
